---
css:  [./cv.css]
output:
  pagedown::html_paged: 
    toc: false
    self_contained: false
    number_sections: false
lot: false
lof: false
toc: false 
knit: pagedown::chrome_print

---

```{r, include=FALSE}
library(tidyverse)
library(here)
library(kableExtra)
library(RefManageR)

knitr::opts_chunk$set(results='asis', echo = FALSE)

RefManageR::BibOptions(bib.style = "authoryear", check.entries = FALSE)
refs <- here("data/publications.bib") %>% ReadBib() %>% as_tibble()

refcounts <- refs %>% count(category) 
refcounts <- refcounts$n %>% set_names(refcounts$category) %>% as.list()

tbl_to_refs <- function(tbl){
  tbl %>% 
    mutate(
      month = as.integer(month),
      year = as.integer(year)
    ) %>% 
    arrange(desc(year), desc(month)) %>% 
    select(-any_of(c("pages", "language", "keywords", "location"))) %>% 
    pmap_chr(function(...){
      tibble(...) %>% as.BibEntry() %>% format(style = "html") 
    }) %>%
    str_remove_all("URL: |In: ") %>% 
    htmltools::HTML()
}

kbl_format <- function(dat){
  dat %>% 
    kbl(format = "html", col.names = NULL, align = "l", escape = FALSE) %>% 
    column_spec(1, width = "120px")
}

get_csv <- function(path){
  path %>% 
    here("data",  .) %>% 
    read_csv(col_names = FALSE, show_col_types = FALSE) 
}

# Note: a known issue with pagedown 
# (see https://github.com/rstudio/pagedown/issues/299)
# is forcing me to manually divide tables interrupted by a page break 
# (overflow content goes into the wrong column by default!)
```

# Kathryn Grace 

| Department of Geography, Environment and Society 
| 558 Social Sciences Building
| 267 19th Avenue S.
| Minneapolis, MN 55455
| <klgrace@umn.edu>

## Education 

| **PhD Geography, University of California, Santa Barbara, 2008**
| Dissertation: “Three Essays on Fertility and Family Planning in Guatemala”
|
| **MA Statistics, University of California, Santa Barbara, 2006**
|
| **MSPH Biostatistics, Tulane University School of Public Health, 2004** 
|
| **BA Theoretical Mathematics, University of California, Berkeley, 2002** 
| *Minor in French Language and Culture*

## Appointments 

```{r}
get_csv("appointments.csv") %>% kbl_format()
```

## Affiliations and Visiting Appointments

```{r}
affiliations <- get_csv("affiliations.csv")
affiliations %>% slice(1:3) %>% kbl_format()
```

\pagebreak

```{r}
affiliations %>% slice(-c(1:3)) %>% kbl_format()
```

## Additional Training

```{r}
get_csv("additional_training.csv") %>% kbl_format()
```

## Fellowships and Honors

| University of Minnesota College of Liberal Arts Scholar of the College, 2019-2022
| Institut National d’Etudes Demographiques Visiting Researcher Fellowship, 2020
| Institut National d’Etudes Demographiques Visiting Researcher Fellowship, 2015 
| Demographic and Health Survey (DHS) Population and Reproductive Health Fellowship, 2007
| University of California Graduate Opportunity Fellowship, 2004-05 & 2007-08
| University of California Department of Geography Block Grant Funding, 2006
| Tulane University School of Public Health Dean’s Grant, 2004
| Tulane University Public Health Traineeship Award, 2003
| University of California Faculty Wives Scholarship, 2001
| University of California Education Abroad Program Scholarship, 1999

\pagebreak

## Grants and Awards 

*Funding amounts reflect amount received by UMN*

::: {.big_table}
```{r}
grants <- here("data/grants.csv") %>% 
  read_csv(show_col_types = FALSE) %>% 
  rowwise() %>% 
  mutate(
    title = paste0("<em>", title, "</em>"),
    when = paste("Award Period:", when)
  ) %>% 
  mutate(
    .keep = "none", 
    X1 = amount,
    X2 = c(title, where, who1, who2, when, note) %>% 
      keep(~!is.na(.x)) %>% 
      paste0(collapse = "<br>")
  ) %>% 
  ungroup() 

grants %>% slice(1:5) %>% kbl_format()
```

\pagebreak

```{r}
grants %>% slice(6:11) %>% kbl_format()
```

\pagebreak

```{r}
grants %>% slice(12:17) %>% kbl_format()
```

\pagebreak

```{r}
grants %>% slice(16:21) %>% kbl_format()
```

\pagebreak

```{r}
grants %>% slice(22:25) %>% kbl_format()
```

:::

# Publications

\*\ indicates postdoctoral researcher or graduate student at the time of submission

## Refereed Articles (`r refcounts$refereed`)

```{r, warning=FALSE}
refs %>% filter(category == "refereed") %>% tbl_to_refs()
```

## Other Publications (`r refcounts$other`)

```{r, warning=FALSE}
refs %>% filter(category == "other") %>% tbl_to_refs()
```

# Presentations 

## Invited Talks 

```{r, warning=FALSE}
refs %>% filter(category == "talks") %>% tbl_to_refs()
```

## Papers Accepted for Presentation at Academic Association Meetings

```{r, warning=FALSE}
refs %>% filter(category == "conference papers") %>% tbl_to_refs()
```

## Posters Accepted for Presentation at Academic Association Meetings

```{r, warning=FALSE}
refs %>% filter(category == "conference posters") %>% tbl_to_refs()
```

# Teaching and Graduate Mentorship 


## Postdoctoral researchers and research scientists

| Andrew Verdin (2018-2020)
| Nina Brooks (2020-2021)
| Jacqueline Banks (postdoctoral trainee MPC) (2019-2021)
| Maya Luetke (2021-ccurrent)
| Jiao Yu (2021-current)

## Committee Chair (Ph.D.)

| Maryia Bakhtsiyarava (co-chair) (completed PhD 2020, beginning postdoctoral fellowship at UC Berkeley, fall 2020)
| Ruthie Burrows
| Grace Cooper
| Oforiwaa Pee Agyei-Boakye (co-chair)


## Committee Membership (Ph.D.)

| Marin Bryce (completed PhD 2018)
| Han Li (completed PhD 2016)
| Jacqueline Banks (completed PhD 2019)
| Kwame Tsikudo (completed PhD 2019)
| Brent Lloyd (completed PhD 2019)
| Aaron Mallory (completed PhD 2020)
| Jacqueline Daigneault (completed PhD 2020) 
| Anna Bolgrien (completed PhD 2021)
| Morrison (Luke) Smith (in progress) 
| Jasper Johnson (in progress)
| Isaac Asante-Wusu (in progress) 

## Committee Chair (Masters):

| Julia Reich (advised until Fall 2018)
| Lori Miles (2014) 
| Delanie Farnham (2015)
| Seth Bogle (advised until Fall 2016) 
| Michael Ryba (advised until Fall 2015)

## Committee Membership (Masters):

| Kaila McDonald (2014)
| Emily Nicolossi (2015) 
| Jessie Bakker (Completed MA, 2020)

## Undergraduate Mentorship: 

| Maximilian Stiefel (honors thesis 2014, currently PhD student at UC Santa Barbara Geography)
| Marc Healy (Undergraduate Research Opportunity Program grant recipient, 2013/14)
| Eddy Urena (Undergraduate Research Opportunity Program grant recipient, 2018)
| Suzanne Scotty (Undergraduate Research Opportunity Program grant recipient, 2020)
| Kassandra Fate (Capstone Project)


## Teaching Experience

| Geography of Health and Health care, University of Minnesota, Department of Geography, Environment and Society, Spring 2016, Spring 2017, Fall 2017, Fall 2018, Fall 2019, Fall 2020
| Global Health Survey Data analysis Spring 2019, Fall 2020, Spring 2021
| Population Geography, University of Minnesota, Department of Geography, Environment and Society, Spring 2017, Fall 2018
| Graduate Seminar: Statistical Methods, University of Minnesota, Department of Geography, Environment and Society, Fall 2017
| Analytic Methods for Population Research, University of Utah, Department of Geography, Fall 2013
| Economic Geography, University of Utah, School of Business, Spring 2013, Spring 2014, Fall 2014, Fall 2015
| Global Development, University of Utah, Department of Geography, Spring 2014
| Advanced Population Geography, University of Utah, Department of Geography, Spring 2013
| Population Geography, University of Utah, Department of Geography, Fall 2012, 2013, 2014, Fall 2015
| Guest Lecturer, Malnutrition and climate in Kenya in Spatial Statistics, Spring 2011
| Guest Lecturer, Fertility Analysis in Spatial Demography, Winter 2010 and Spring 2012 
| Teaching Assistant, Center for Spatially Integrated Social Sciences (CSISS) -  Spatial Perspectives on Analysis for Curriculum Enhancement (SPACE), UCSB, 2005 - 2007
| Graduate Research Mentor (high school summer outreach program), UCSB, 2005 - 2007
| Teaching Assistant, Human Geography, UCSB, Summer 2007
| Guest Lecturer, Global trends in Fertility for Population Geography, Winter 2007
| Teaching Assistant, Center for Spatially Integrated Social Sciences (CSISS) -  Population Science Summer Workshop, UCSB, 2005 - 2006
| Teaching Assistant, Population Geography, UCSB, Fall 2005
| Teaching Assistant, Introductory Statistics, UCSB, 2004 - 2005

# Professional Service 

## Discipline

| Deputy Editor Demography July 2022-
| Editorial Board Discover Social Science and Health Journal 2021-
| Editorial Board Computers, Environment and Urban Systems Journal 2020-
| Editorial Board CABI Agriculture and Biosciences Journal 2021
| Editorial Board Spatial Demography 2018-
| Editorial Board Population and Environment 2018-
| Chair, Population and Environment Research Network 2021-
| President, Population Specialty Group American Association of Geographers 2019-2022
| Co-guest editor, Frontiers - Gender and social consideration in climates and impacts research 2020-2022
| Advisory Board Population Environment Research Network 2019-2021
| Organizing Committee Population Association of America Annual Meeting 2020
| Session Organizer - Population Association of America Annual Meeting 2019
| Session Chair - Population Association of America Annual Meeting 2018, 2022
| Discussant - Population Association of America Annual Meeting 2018, 2022
| Guest Editor Population and Environment - Special Issue 2018-2019
| Vice-President, Population Specialty Group American Association of Geographers 2017-2019
| Guest Editor Population and Environment 2018 and 2020
| Discussant - Population Association of America Annual Meeting 2015
| Student Poster Judge - American Geophysical Union Annual Meeting 2014
| Session Co-Organizer - Population Association of America Annual Meeting 2014

## University of Minnesota

| Diversity, equity and inclusion Committee Chair, Department of GES (2020-2021)
| MPC Senior Faculty Search Committee, Minnesota Population Center (2018-2019)
| GIS Faculty Search Committee co-Chair, Department of GES (2019)
| Ad-hoc Merit Review Committee, Department of GES (2018-2019)
| Merit Committee Chair, Department of GES (2018-2019)
| Grievance Committee Chair, Department of GES (2018-2019 & 2020-2021)
| Coffee Hour/Brown Day Organizing Committee Chair - Department of GES (2017-2018)
| Graduate Education Policy Committee - Department of GES (2017-2020)
| Admissions Committee - Department of GES (2016-2017)
| Executive Committee -  Department of GES (2016-2018)
| Advisory Board Member - DASH (2018-current)
| Fulbright Grant Reviewer (UMN) - (2017-2018)
| Graduate Travel Grant Reviewer - (2017-2019)
| Graduate School Advisory Board Member (2016-2019)
| Advisory Board Member - Minnesota Population Center (2016-2019)
| Co-Organizer (with Miranda Joseph) of Counter Accounting Workshop (2017)
| Grants and Awards committee - Department of GES 2016
| Parenting Across Roles, Invited Panelist Fall 2016
| Parenting in Academia, Invited Panelist Spring 2016

## University of Utah

| Moderator - University of Utah, Undergraduate Research Conference 2014
| College of Social and Behavioral Sciences, Appeals Committee 2013 - 2015
| Department of Geography, Graduate Committee 2013 - 2015
| Department of Geography, Colloquia Committee 2012 - 2015

## Professional Membership 

| Association of American Geographers
| American Geophysical Union
| Population Association of America
| American Statistical Association

## Reviewer 

| Nature Energy
| Nature Sustainability (x3)
| Nature Climate Change
| Nature Communication
| Proceedings of the National Academy of Sciences
| Science
| Lancet Planetary Health (x2)
| Demography (x4)
| American Sociological Review
| American Journal of Public Health
| Population and Development Review (x2)
| Scientific Data
| Food Policy
| Annals of the American Association of Geographers
| American Journal of Agricultural Economics
| Global Environmental Change (x3)
| Global Change Biology
| Population and Environment (x6)
| Spatial Demography (x2)
| Population (French Language) (x2)
| International Regional Science Review
| Scientific Reports
| Health and Place
| BMC Nutrition
| Public Health Nutrition
| Social Science and Medicine
| International Perspectives on Sexual and Reproductive Health (x2)
| PLOS One (x3)
| Remote Sensing Applications: Society and Environment
| Health Science Journal
| Health and Place
| International Journal of Disaster Risk Reduction
| Landscape Ecology
| Health Education Journal
| Applied Geography (x4)
| Pan American Journal of Public Health (x3)
| Remote Sensing
| Urban Studies
| Population Review
| NASA LCLUC ROSES
| Ad-hoc NIH review panel (CHHD-W), 2021, 2022
| Swiss National Science Foundation (x2)
| NASA Postdoctoral Program
| National Science Foundation
| EPA Star Graduate Student Fellowship
| U of U Air Quality Program Seed Grant Funding Opportunity
| NASA SERVIR Applied Sciences Grant Opportunity
| JPI (Joint Programming Initiative) "Connecting Climate Knowledge for Europe"

## Community Service 

| Santa Barbara Charter School Parent Volunteer, 2011-2012
| Goleta Family School Parent Volunteer and Goleta Earth Day co-Organizer, 2006 - 2008
| Tulane University School of Public Health Student Health Representative, 2003 - 2004
| UC Berkeley Student Parent Organization Treasurer, 2001 - 2002
| UC Berkeley Family Student Housing Health Worker, 2001 - 2002

## Languages and Skills 

French, SAS, SPSS, R, ArcGIS, LaTeX